Quantitative Benchmarking for Conjecture Generation

### 2018-04-23 PhDSymposium2018/abstract.tex
Symposium 2018 abstract tweaks

\emph{Conjecture generation} (CG) is the open-ended task of conjecturing
``interesting'' properties of a given logical theory (such as a software
library), and is studied as a sub-field of \emph{mathematical theory
  exploration}. Such conjectures can be sent to automated theorem provers (ATP),
have helped prove software correctness by finding key
lemmas~\cite{Claessen.Johansson.Rosen.ea:2013}. Automating formal methods this
way can reduce the cost and difficulty which have historically limited their use
to mission- or life-critical domains. More practical automated reasoning shows
promise in software
engineering~\cite{McKinna:2006,chlipala2011certified,Xi2003}, automated research
``assistants''~\cite{McCarthy_Programs59,lenat:77,benzmuller1997omegamega} and
educational software~\cite{conf/ijcai/TrybulecB85,hendriks2010teaching}.

@@

  \caption{Time taken for CG on samples from TIP, with 300 second timeout. Lines
    show medians and error bars show inter-quartile range, with 31 samples of
    each size except 1 (14) and 2 (30). }
  \label{figure:quickspec_runtimes}
\end{figure}

@@

The aim of CG is to read such definitions and produce a set of ``interesting''
properties which they appear to satisfy. This can help formalise the
``background knowledge'' required for proving, and present the user with ideas
they hadn't considered.

@@

Their running times are shown in Figure~\ref{figure:quickspec_runtimes}, for
sample of up to 20 functions. The measurements are paired, and we followed the
Speedup-Test protocol of Touati, Worms and Briais~\cite{touati2013speedup} to
find that \textsc{QuickSpec} was faster for $67\%-98\%$ of sizes (with 95\%
confidence). Only sizes 1 and 2 weren't significantly faster, due to too few
samples. Timeouts bounding the difference make this a conservative estimate.

>>>>

\emph{Conjecture generation} (CG) is the open-ended task of conjecturing
``interesting'' properties of a given logical theory (such as a software
library), and is studied as a sub-field of \emph{mathematical theory
  exploration}. Such conjectures can be sent to automated theorem provers (ATP),
and have helped software correctness proofs by finding key
lemmas~\cite{Claessen.Johansson.Rosen.ea:2013}. Automating formal methods this
way can reduce the cost and difficulty which have historically limited their use
to mission- or life-critical domains. More practical automated reasoning shows
promise in software
engineering~\cite{McKinna:2006,chlipala2011certified}, automated research
``assistants''~\cite{McCarthy_Programs59,lenat:77,benzmuller1997omegamega} and
educational software~\cite{conf/ijcai/TrybulecB85,hendriks2010teaching}.

@@

  \caption{CG running time on definitions sampled from TIP (31 of each size,
    except 1 (14) and 2 (30)). Failures (out-of-memory or 300 second timeout)
    shown in red. Lines show medians, error bars are inter-quartile range.}
  \label{figure:quickspec_runtimes}
\end{figure}

@@

The aim of CG is to read such definitions and produce a set of ``interesting''
properties which they appear to satisfy. This can help formalise the
``background knowledge'' required for proving, and present users with novel
ideas.

@@

Their running times are shown in Figure~\ref{figure:quickspec_runtimes}, for
samples of up to 20 functions. The measurements are paired, and we followed the
Speedup-Test protocol of Touati, Worms and Briais~\cite{touati2013speedup} to
find that \textsc{QuickSpec} was faster for $67\%-98\%$ of sizes (with 95\%
confidence). Only sizes 1 and 2 weren't significantly faster, due to too few
samples. This is also conservative, since the difference is bounded by the
timeout.
